Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-03 paper.qmd
Best and bad fit for S-curve

<!--change the tuning parameter-->

>>>>

<!--add more details regarding to the how the change happening with different number of bins-->

<!--best model-->
<!--need to mention why it is the best-->

<!--bad model-->
<!--need to mention why it is the bad-->
<!--Not represented the whole data structure beacuse there are some discontinuity in the S-curve-->
<!-- Why? bad

<!-- add MSE values for the screenshot figure names-->
